---
title: "Second Round of Assigning Articles to Evaluators"
author: "Adam H. Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Second Round of Assigning Articles to Evaluators}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Creating a sample of articles

As a second round to bring the analysis up-to-date, we elected to sample 100 articles from the same 21 journals for 2017-2018.

Aside from the different years, the journals remain the same and process as described previously.

## Step 1

### R setup

```{r library, message=FALSE}
library("dplyr")
library("readr")
library("bib2df")
library("googlesheets4")
library("stringr")
library("Reproducibility.in.Plant.Pathology")

set.seed(23)

# For printing tibble in total
options(tibble.print_max = 21, tibble.print_min = 21)
```

### Create list of journals

We hand-picked a list of 21 journals that we felt represented plant pathology research.
In this step, we will create a `tibble` in R of these journals, assigning them a number so that we can randomise them.

```{r journal_list}
journal_list <- tibble(
  seq(1:21),
  c("Australasian Plant Pathology",
    "Canadian Journal of Plant Pathology",
    "Crop Protection",
    "European Journal of Plant Pathology",
    "Forest Pathology",
    "Journal of General Plant Pathology",
    "Journal of Phytopathology",
    "Journal of Plant Pathology",
    "Virology Journal (Plant Viruses Section)",
    "Molecular Plant-Microbe Interactions",
    "Molecular Plant Pathology",
    "Nematology",
    "Physiological and Molecular Plant Pathology",
    "Phytoparasitica",
    "Phytopathologia Mediterranea",
    "Phytopathology",
    "Plant Disease",
    "Plant Health Progress",
    "Plant Pathology",
    "Revista Mexicana de Fitopatología",
    "Tropical Plant Pathology"))

names(journal_list) <- c("number", "journal")
```

### Create list of evaluators for second round of reviews

These articles were added at a later date to look for any possible trends in the plant pathology literature being published.
The same journal titles were sampled for 2017-2018 using the same protocols as the original set of 200 articles for 100 articles over two years.

```{r new_assignees}
assignees <- rep(c("Emerson", "Kaique"), 50)
```

### Create randomised list

In this round only two individuals evaluated the articles, so we will create a randomised list of journal articles to assign to these two authors.

#### Create a randomised list of the journals

```{r journal_sample}
journals <- tibble(sample(1:21, 100, replace = TRUE))

names(journals) <- "number"

journals <- left_join(journals, journal_list, "number")
```

#### Randomly select articles

Generate a random list of years between 2012 and 2016 and a random list of start pages between 1 and 150 since some journals start numbering at 1 with every issue.
Then bind the columns of the randomised list of journals with the randomised years and page start numbers.
This then assumes that there is no temporal effect, _i.e._, the time of year an article is published does not
affect whether or not it is reproducible.

```{r years_and_articles}
year <- sample(2017:2018, 100, replace = TRUE)

contains_page <- sample.int(150, 100, replace = TRUE)

journals <- cbind(journals[, -1], year, contains_page, assignees)

journals <- arrange(.data = journals, assignees, journal, year, contains_page)
```

#### Check the number of articles per journal

```{r, count}
journals %>%
  group_by(journal) %>%
  tally(sort = TRUE)
```

Once this is done, the articles are manually examined for suitability.
Reference articles or off-topic articles are not included.
Notes are provided regarding these cases in `assigned_article_notes`.
If the selected page number/article was not suitable, the next sequential article was selected manually.

### Add empty columns for evaluations

A variety of information will be collected with each article to be used in the analysis later.
It is easiest to enter this using a spreadsheet application, so we will add on the columns for what information we want to collect and save the table as a CSV for manual editing.

```{r}
to_record <- c(
  "doi",
  "IF_5year",
  "country",
  "open",
  "repro_inst",
  "iss_per_year",
  "art_class",
  "supl_mats",
  "comp_mthds_avail",
  "software_avail",
  "software_cite",
  "analysis_auto",
  "data_avail",
  "data_annot",
  "data_tidy",
  "reproducibility_score"
  )
  journals[to_record] <- ""
  
  template <- 
    journals %>%
    group_by(assignees) %>%
    as_tibble()
```

### Write to Google Sheets

We decided to use Google Sheets so that we could concurrently edit the file more easily.
Once we're done filling in our evaluations, we will import the data back to R.
Jenny Bryan has created a handy package, _googlesheets4_ that we use here.
_Note that this must be run interactively for `gs_new()` to work.
Knitting this .Rmd file will not generate any Google sheets, it must be done in an interactive R session._

Create a Google Sheets workbook to hold worksheets for this project.
This first sheet will serve as a template and is thus named "template".

```{r setup_gs, eval=FALSE}
# Give googlesheets permission to access spreadsheets and Google Drive
gs4_auth()

# create Google Sheet for concurrent edits, first sheet: article notes template
gs4_create(
  "article_notes_2017-2018",
  sheets = template
  )
```

## Step 2

### Add article DOI's

This step is completed in Google's online Sheets app, Adam looked up articles and added notes and DOIs to a sheet, "article_notes_2017-2018" which will be imported to R in the next step.

## Step 3

### Generate a bibliography file to use with the paper

Using the DOIs in this file, we can retrieve the BibTex citations for those articles that provide a DOI.
Note that not all of the selected articles have a DOI, so we'll have to manually generate those entries, or fetch them from the journals' websites later.

```{r join_files, warning=FALSE, message=FALSE, results="hide", eval=FALSE}
notes <- drive_get("article_notes_2017-2018") %>%
  read_sheet()
  
# format DOIs to all be uniform, lower-case
notes$doi <- tolower(notes$doi)

# convert encodings for text with accents
notes$journal <- iconv(notes$journal, "latin1", "UTF-8") 

# get bib references from the DOI (that exist)
bib <- unlist(lapply(notes$doi, doi2bib))
```

The _Journal of Plant Pathology_ does not supply valid bib entries via the DOI.
So we need to clean them up.

```{r first_bib_cleaning, warning=FALSE, message=FALSE, results="hide", eval=FALSE}

# locations of Journal of "Plant Pathology"" entries in bib object
clean_pp <- grep("journal=\\{Journal of Plant Pathology\\}", bib)

# create a dataset of just those bib entries
bib_clean_pp <- bib[clean_pp]

# function to clean the entries
clean_articles_pp <- function(x) {
  title_loc <- unlist(gregexpr(pattern = "title", x))
  y <- substr(x, start = title_loc[1], stop = nchar(x))
  y <- paste0("@article{jpp,\n\t" , y)
  y <- gsub("}, ", "},\n\t", y)
  y <- gsub("=", " = ", y)
  y <- gsub("}}\n", "}\n}", y)
}

# apply function and clean the bib entries
cleaned_pp <- unlist(lapply(bib_clean_pp, clean_articles_pp))

# remove the incorrect entries for Journal of Plant Pathology
bib <- bib[-clean_pp]
```

_Phytopathologia Mediterranea_ also provides some malformed bib entries.
The cite entries are malformed and `<em> </em>` is used rather than the proper `\textit{}` for a BibTeX file.

```{r second_bib_cleaning, warning=FALSE, message=FALSE, results="hide", eval=FALSE}
clean_pm <- grep("journal=\\{Phytopathologia Mediterranea\\}", bib)
bib_clean_pm <- bib[clean_pm]
clean_articles_pm <- function(x) {
  x <- gsub(" @article\\{[[:print:]]+, title=\\{", "@article\\{PM, title = \\{", x)
  x <- gsub("<em>", "\\\textit\\{", x)
  x <- gsub("</em>", "}", x)
  }

# apply function and clean the bib entries
cleaned_pm <- unlist(lapply(bib_clean_pm, clean_articles_pm))
bib <- bib[-clean_pm]
```

The larger list of bib objects has some items that are supposedly invalid DOIs.
In this step we remove them and clean up the list. They'll be added back to the database when we merge the notes at the end.

Also there are duplicates in the list somehow. Use `unique()` to clean the list up.

```{r, clean_bib, eval=FALSE}
bib <- bib[bib != "Invalid DOI"]

bib <- unique(bib)
```

Next export the items as files to disk as .bib files to be cleaned using JabRef.
This will automatically assign unique cite keys and fix some issues with characters in the bib file.
Open the file in JabRef and click "yes" when prompted to regarding the cite keys.

```{r export_import_bib, eval=FALSE}
# clean up any existing files since we're appending
unlink("~/tmp/bib_new_article_notes.bib")

# write files to a local directory and clean up with JabRef
lapply(unlist(bib),
       write, "~/tmp/bib_new_article_notes.bib",
       append = TRUE)
lapply(unlist(cleaned_pp),
       write, "~/tmp/bib_new_article_notes.bib",
       append = TRUE)
lapply(unlist(cleaned_pm),
       write, "~/tmp/bib_new_article_notes.bib",
       append = TRUE)
```

*Important* Open resulting files in `~/tmp` directory in JabRef, create new keys and resave.
JabRef will generate unique keys and fix any inconsistencies that may exist from the DOI search.

### Export Google Sheets

In this last bit, import the BibTeX file back into R and export to a tab in the Google Sheets for collaborative edits.

```{r google, warning=FALSE, message=FALSE, results="hide", eval=FALSE}

# import both the Journal of Plant Pathology (cleaned_bib) and article_notes.bib
bib <- bib2df("~/tmp/bib_new_article_notes.bib")
names(bib) <- tolower(names(bib))

# join notes with bibliographic data
bib_df <- left_join(notes, bib)
bib_df <- arrange(bib_df, new_assignees)

# create Google Sheet for concurrent edits
new_article_notes <-
  new_article_notes %>%
  gs_ws_new(
    ws_title = "new_article_evaluations",
    input = bib_df,
    trim = TRUE,
    verbose = FALSE
  )

# clean up files to build R package properly with no NOTES
unlink(".httr-oauth")
```

### Last steps

The last few steps are completed outside of R in Google Sheets, manually adding the missing information to the spreadsheet and the new assignees adding their evaluations of their respective articles.

The Google Sheets file can be found here:
<https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381>.

# Colophon

```{r sessioninfo}
sessioninfo::session_info()
```
