---
title: "Retrieving References Using DOI"
author: "Adam H. Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{retrieving_references}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Load the DOIs

Load DOIs from the gsheet template used to create the notes file.
The DOIs were recorded when the initial articles were assigned.

```{r get-sheet, message=FALSE, warning=FALSE, eval=FALSE}
doi <-
  googlesheets4::read_sheet(
    "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1579463541"
  )
```

## Some journals do not provide a DOI!

For some reason, even now, some journals are not minting DOIs. Those journals will be removed from the automated search for references.
They will be manually added later.

```{r remove-na, message=FALSE, eval=FALSE}
doi <- na.omit(doi$doi)
```

## Get the bibtex entries

```{r get-bib-entry, message=FALSE, eval=FALSE}
sink("references.bib")
bib <- sapply(doi, rcrossref::cr_cn)
sink()
```

## Print the references.

```{r write-bib-file, message=FALSE, eval=FALSE}
file <- "references.bib"
df_references <- bib2df::bib2df(file)
df_references
```
