---
title: "Analysis"
author: "Adam H. Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
knitr::opts_chunk$set(fig.width = 6.4, fig.height = 6.4)
```

This analysis is a simple visualisation and tabulation of the data gathered from surveying 21 journals and 300 articles in the field of plant pathology for their openness and reproducibility.

# Set-up Workspace

Load libraries used and setting the ggplot2 theme for the document.

```{r load-libraries}
library("tidyverse")
library("ggpubr")
library("janitor")
library("pander")
library("Reproducibility.in.Plant.Pathology")
theme_set(theme_pubclean())
```

## Import the data and calculate the reproducibility score

```{r}
rrpp <- import_notes()
```

## Reproducibility score

The reproducibility score was calculated as the sum of the scores for computational method availability for the total available scores.
That is, if a paper did not require specialised software but deposited and reported all data the score was 100%, the same as for another article that cited and used all open source software and deposited code and data.

```{r}
ggplot(rrpp, aes(x = reproducibility_score)) +
  geom_density() +
  ggtitle("Reproducibility Score") +
  xlab("Score (%)")
```

## Evaluator effect on reproducibility score

Have a look at whether evaluators had an effect on the scores assigned.

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = assignee)) +
  geom_count() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ggtitle("Evaluator Effect") +
  ylab("Reproducibility Score (%)") +
  xlab("Evaluator") +
  labs(caption = "Crossbar indicates median reproducibility score value.")
```

# Visualise evaluations

## Article classes

What class did the articles fall into, "Applied" or "Fundamental".

```{r}
ggplot(rrpp, aes(y = art_class)) +
  geom_bar() +
  ylab("Class") +
  ggtitle("Article Classification")
```

## Computational methods available

Were the computational methods, scripts, source code, _etc._, made available?

```{r}
ggplot(rrpp, aes(y = as.factor(comp_mthds_avail))) +
  geom_bar() +
  ggtitle("Computational Methods Availability") +
  ylab("Score") +
  labs(caption = "NA means that no computational methods were used to generate the data,\ne.g. only PCR results reported with no statistical analysis")
```

## Software availability

Were the software used readily available and preferably open-source?

```{r}
ggplot(rrpp, aes(y = software_avail)) +
  geom_bar() +
  ggtitle("Software Availability") +
  ylab("Score")
```

## Software citations

Were the software that was used properly cited?

```{r}
ggplot(rrpp, aes(y = software_cite)) +
  geom_bar() +
  ggtitle("Software Cited") +
  ylab("Score")
```

## Software used (cited)

Count and sort top 10 software packages cited.
There are likely others that are used, but they have not been properly cited or listed by the authors.

First create a tidy data frame of the data by unnesting software used as in many cases multiple software packages were used, so will end up with multiple rows for same article, one for each software.

```{r}
rrpp_software <-
  rrpp %>%
  transform(software_used = strsplit(software_used, ",")) %>%
  unnest(software_used) %>%
  mutate(software_used = trimws(software_used)) %>%
  mutate(software_used = toupper(software_used)) # convert all to uppercase to standardise
```

Now graph the top ten software packages used.

```{r}
tab <- table(rrpp_software$software_used)
tab_s <- sort(tab)
top10 <-
  tail(names(tab_s), 14) # checking the table, there are several ties
top_software <- subset(rrpp_software, software_used %in% top10)
top_software$software_used <- factor(top_software$software_used,
                                     levels = rev(top10))

ggplot(top_software, aes(y = software_used)) +
  geom_bar() +
  ggtitle("Top 10 Software Used") +
  xlab("Count") +
  ylab("Software")
```

## Data availability

Were the data made readily available?

```{r}
ggplot(rrpp, aes(y = data_avail)) +
  geom_bar() +
  ggtitle("Data Availability") +
  ylab("Score")
```

## Article class effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = art_class)) +
  geom_count() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ggtitle("Article Class Effect") +
  ylab("Reproducibility Score (%)") +
  xlab("Class") +
  labs(caption = "Crossbar indicates median reproducibility score value.")
```


## Journal effect on reproducibility score

```{r}
ggplot(rrpp, aes(x = reproducibility_score,
                 y = abbreviation)) +
  geom_count() +
  ggtitle("Journal Effect") +
  ylab("Journal") +
  xlab("Score")
```


## Five year impact factor effect on reproducibility score

```{r, message=FALSE}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = IF_5year)) +
  geom_count() +
  geom_smooth() +
  ggtitle("Five Year IF Effect") +
  ylab("Score") +
  xlab("Impact Factor")
```

## Journal open access effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(open))) +
  geom_count() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ggtitle("Journal Open Access Classification Effect") +
  ylab("Score") +
  xlab("Open Access Classification") +
  labs(caption = "Crossbar indicates median score value.")
```

## Journal reproducibility instructions effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(repro_inst))) +
  geom_count() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ggtitle("Reproducibility Instructions Effect") +
  ylab("Reproducibility Score (%)") +
  xlab("Reproducibility Instructions Score") +
  labs(caption = "Crossbar indicates median score value.")
```

## Scores by year

## Full reproducibility score

```{r, message=FALSE}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = year)) +
  geom_count() +
  geom_smooth() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ylab("Reproducibility Score (%)") +
  xlab("Year") +
  labs(caption = "Crossbar indicates median score value.")
```

## Computational methods score

```{r, message=FALSE}
ggplot(rrpp, aes(y = comp_mthds_avail,
                 x = year)) +
  geom_count() +
  geom_smooth() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ylab("Computational Methods Availability") +
  xlab("Year") +
  labs(caption = "Crossbar indicates median score value.")
```

## Software availability

```{r, message=FALSE}
ggplot(rrpp, aes(y = software_avail,
                 x = year)) +
  geom_count() +
  geom_smooth() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ylab("Software Availability") +
  xlab("Year") +
  labs(caption = "Crossbar indicates median score value.")
```

## Data availability

```{r, message=FALSE}
ggplot(rrpp, aes(y = data_avail,
                 x = year)) +
  geom_count() +
  geom_smooth() +
  stat_summary(
    fun = median,
    fun.min = median,
    fun.max = median,
    geom = "crossbar",
    width = 0.5
  ) +
  ylab("Data Availability") +
  xlab("Year") +
  labs(caption = "Crossbar indicates median score value.")
```

# Tables

## Table of journals surveyed

```{r journals}
rrpp_journals <- tabyl(rrpp, journal)[, -3]
names(rrpp_journals) <- c("Journal", "n")
pander(rrpp_journals)
```

## Table of article scores

```{r table_scores}
article_scores <- tabyl(rrpp, reproducibility_score)
names(article_scores) <- c("Score", "n", "Percent")
article_scores$Percent <- round(article_scores$Percent * 100, 1)
pander(article_scores)
```
