---
title: "Analysis"
author: "Adam H Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

This analysis is a simple visualisation and tabulation of the data gathered from surveying 21 journals and 200 articles in the field of plant pathology for their openness and reproducibility.

# Setup Workspace

Setup workspace by loading libraries used and setting the ggplot2 theme for the document.

```{r load-libraries}
library(dplyr)
library(ggplot2)
library(hrbrthemes)
library(janitor)
library(magrittr)
library(pander)
library(Reproducibility.in.Plant.Pathology)
library(tidyr)

theme_set(theme_ipsum_rc())
```

# Import article evaluations

```{r}
rrpp <- gsheet::gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
)
```

## Prepare the data

Calculate the reproducibility score, dropping any rows (in this case two) that have `NA` for the full score and convert fields to factors and the tibble to a data.frame.

```{r}
rrpp <-
  rrpp %>%
  mutate(
    reproducibility_score =
      if_else(
        condition = data_avail > 0,
        
        true = as.integer(comp_mthds_avail) +
          as.integer(software_avail) +
          as.integer(software_cite) +
          as.integer(data_avail),
        
        false = as.integer(data_avail),
        
        missing = as.integer(0)
      )
  ) %>%
  mutate(IF_5year =
           if_else(
             condition = is.na(IF_5year),
             true = 0,
             false = IF_5year
           )) %>%
  mutate(art_class = as.factor(art_class)) %>%
  mutate(repro_inst = as.factor(repro_inst)) %>%
  mutate(open = as.factor(open)) %>%
  mutate(abbreviation = as.factor(abbreviation)) %>%
  mutate(assignee = as.factor(assignee)) %>%
  filter(!is.na(reproducibility_score)) %>%
  as.data.frame()
```

Create a tidy data frame of the data by unnesting software used as in many cases
multiple software packages were used, so will end up with multiple rows for same
article, one for each software.

```{r}
rrpp_software <- 
  rrpp %>%
  unnest(software_used = strsplit(software_used, ", "))
```

# Visualise evaluations

## Article classes

What class did the articles fall into, "Applied, 

```{r}
ggplot(rrpp, aes(x = art_class)) +
  geom_bar(stat = "count") +
  xlab("Class(es)") +
  ggtitle("Article Classification") +
  coord_flip()
```

## Computational methods available

Were the computational methods, scripts, source code, etc. made available?

```{r}
ggplot(rrpp, aes(x = comp_mthds_avail)) +
  geom_bar() +
  ggtitle("Computational Methods Availability") +
  xlab("Score") +
  coord_flip()
```

## Software availability

Were the software used readily available and preferably open-source?

```{r}
ggplot(rrpp, aes(x = software_avail)) +
  geom_bar() +
  ggtitle("Software Availability") +
  xlab("Score") +
  coord_flip()
```

## Data availability

Were the data made available?

```{r}
ggplot(rrpp, aes(x = data_avail)) +
  geom_bar() +
  ggtitle("Data Availability") +
  xlab("Score") +
  coord_flip()
```

## Software citations

Were the software that was used properly cited?

```{r}
ggplot(rrpp, aes(x = software_cite)) +
  geom_bar() +
  ggtitle("Software Cited") +
  xlab("Score") +
  coord_flip()
```

## Software used (cited)

Count and sort top 10 software packages cited. There are likely others that are
used, but they have not been properly identified by the authors.

```{r}
tab <- table(rrpp_software$software_used)
tab_s <- sort(tab)
top10 <- tail(names(tab_s), 17) # checking the table, there are several ties
top_software <- subset(rrpp_software, software_used %in% top10)
top_software$software_used <- factor(top_software$software_used,
                                     levels = rev(top10))

ggplot(top_software, aes(x = software_used)) +
  geom_bar() +
  ggtitle("Top 10 Software Used") +
  xlab("Software") +
  ylab("Count") +
  coord_flip()
```

## Reproducibility score

The reproducibility score was calculated as the sum of the scores for computational
method availability, 

```{r}
ggplot(rrpp, aes(x = reproducibility_score)) +
  geom_bar() +
  ggtitle("Combined Reproducibility Score") +
  xlab("Score") +
  coord_flip()
```

## Article class effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = art_class)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Article Class Effect") +
  xlab("Class(es)") +
  ylab("Score") +
  coord_flip()
```

## Journal effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = abbreviation)) +
  geom_count() +
  ggtitle("Journal Effect") +
  xlab("Journal") +
  ylab("Score") +
  coord_flip()
```

## Evaluator effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = assignee)) +
  geom_count() +
  ggtitle("Evaluator Effect") +
  xlab("Evaluator") +
  ylab("Score") +
  coord_flip()
```

## Five year impact factor effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = IF_5year)) +
  geom_count() +
  ggtitle("Five Year IF Effect") +
  xlab("Impact Factor") +
  ylab("Score") +
  coord_flip()
```

## Journal open access effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = open)) +
   geom_count() +
  ggtitle("Open Access Effect") +
  xlab("Open Access Classification") +
  ylab("Score") +
  coord_flip()
```

## Journal reproducibility instructions effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(repro_inst))) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Reproducibility Instructions Effect") +
  xlab("Reproducibility Instructions Score") +
  ylab("Score") +
  coord_flip()
```

## Tables

### Table of Journals Surveyed

```{r}
rrpp_journals <- tabyl(rrpp, journal)
names(rrpp_journals) <- c("Journal", "n", "Percent")
rrpp_journals$percent <- rrpp_journals$percent * 100
pander(rrpp_journals)
```

### Table of Article Scores

```{r table_scores}
article_scores <- tabyl(rrpp, reproducibility_score)
names(article_scores) <- c("Score", "n", "Percent")
pander(article_scores)
```

