---
title: "Inter-rater Repeatability"
author: "Adam H. Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inter-rater Repeatability}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{tidyverse}
  %\VignetteDepends{pander}
  %\VignetteDepends{ggridges}
  %\VignetteDepends{patchwork}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(fig.width = 6.4, fig.height = 6.4)
```

This vignette documents the analysis of the data gathered from surveying 5 journal articles, which all five authors evaluated for an inter-rater comparison.
Five articles were evaluated by all five authors to understand the differences between ratings assigned by each of the paper's authors.
All original scores are kept with corrections being made to the `software_avail` column in `software_avail_corrected` (by AHS) based on the software that was recorded as being used in each paper.
This step removes some disagreement between the ratings.

# Set-up Workspace

Load libraries used and setting the *ggplot2* theme for the document.

```{r load-libraries, message=FALSE}
library(patchwork)
library(ggridges)
library(tidyverse)
library(pander)
library(Reproducibility.in.Plant.Pathology)

theme_set(theme_classic())
```

## Import Data

Import the data and print.

```{r import-rrpp}
rrpp <- import_interrater_scores()
pander(rrpp)
```

## Article Classifications

```{r article-classifications}
a <- ggplot(rrpp, aes(x = molecular,
                      colour = molecular,
                      fill = molecular)) +
  geom_bar(position = "dodge") +
  ylab("") +
  xlab("") +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()  #remove y axis ticks
  ) +
  ggtitle("Molecular Focus") +
  facet_grid(doi ~ assignee) +
  theme(legend.position = "top")

b <- ggplot(rrpp, aes(x = art_class,
                      colour = art_class,
                      fill = art_class)) +
  geom_bar(position = "dodge") +
  ylab("") +
  xlab("") +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) +
  ggtitle("Article Class") +
  facet_grid(doi ~ assignee) +
  theme(legend.position = "top")

p <- (a | b)
p
```


## Reproducibility Criteria

```{r reproducibility-scores}
c <- ggplot(rrpp,
            aes(y = doi,
                x = software_cite)) +
  xlab("") +
  xlim(c(0, 3)) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  geom_density_ridges() +
  ggtitle("Software Citation")

d <- ggplot(rrpp,
            aes(y = doi,
                x = software_avail)) +
  ylab("") +
  xlab("") +
  geom_density_ridges() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  ) +
  xlim(c(0, 3)) +
  ggtitle("Software Availability")

e <- ggplot(rrpp,
            aes(y = doi,
                x = comp_mthds_avail)) +
  geom_density_ridges() +
  xlim(c(0, 3)) +
  ggtitle("Computational Methods Availability")

f <- ggplot(rrpp,
            aes(y = doi,
                x = data_avail)) +
  ylab("") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlim(c(0, 3)) +
  geom_density_ridges() +
  ggtitle("Data Availability")

p <- (c | d) / (e | f)
p
```

## Reproducibility Scores

Look at agreement of the reproducibility scores across evaluators with corrected `software_avail` ratings, `software_avail_corrected`.

```{r repro-scores}
ggplot(rrpp,
       aes(y = doi,
           x = reproducibility_score)) +
  geom_density_ridges() +
  xlim(c(0, 100))
```

## Software Used

We can check if most authors found the same software in the papers that were evaluated.
Perfect agreement is a 5, below that the software was not clearly and easily detected by the evaluator.

```{r software-table}
rrpp_software <-
  rrpp %>%
  transform(software_used = strsplit(software_used_cleaned, ",")) %>%
  unnest(software_used) %>%
  mutate(software_used = trimws(software_used)) %>%
  mutate(software_used = toupper(software_used))

tab <- table(rrpp_software$software_used)
tab_s <- as.data.frame(sort(tab))
tab_s <-
  tab_s %>%
  arrange(desc(Freq)) %>%
  rename("Software" = "Var1", "Frequency" = "Freq")

pander(tab_s)
```

# Colophon

```{r sessioninfo}
sessioninfo::session_info()
```
