---
title: "Analysis of Article Class Effect"
author: "Adam H. Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis of Article Class Effect}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{brms}
  %\VignetteDepends{bayestestR}
  %\VignetteDepends{bayesplot}
  %\VignetteDepends{ggplot2}
  %\VignetteDepends{here}
  %\VignetteDepends{pander}
  %\VignetteDepends{sessioninfo}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(fig.width = 6.4, fig.height = 6.4)
```

This vignette documents a simple visualisation and tabulation of the data gathered from surveying 21 journals and 300 articles in the field of plant pathology for their openness and reproducibility.

# Set-up Workspace

Load libraries used and setting the _ggplot2_ theme for the document.

```{r load-libraries, message=FALSE}
library("brms")
library("bayestestR")
library("bayesplot")
library("ggplot2")
library("here")
library("pander")
library("Reproducibility.in.Plant.Pathology")

options(mc.cores = parallel::detectCores())
theme_set(theme_classic())
```

## Import Data

Data are imported and the base level is set to Molecular Plant Pathology, the journal with the highest five-year impact factor that will be used as the intercept in the following models.

```{r}
rrpp <- import_notes()
```

## Notes

All models are using the same priors.
Because of the amount of zero values in the `reproducibility_score` a `hurdle_gamma()` family is used for all models as well.

### Priors

The priors are fairly flat.

```{r priors}
priors <- prior_string("normal(0, 10)")
```

## Article Class Model

Test the effect that the article's class, `applied` or `fundamental` had on the reproducibility score.
Here, `art_class` is a fixed effect, `year` and `assignee` are assigned as random effects.

```{r article-class}
m2 <-
  brm(
    formula = reproducibility_score ~  art_class + (1 | year) + (1 | assignee),
    data = rrpp,
    seed = 25,
    prior = priors,
    family = hurdle_gamma(),
    control = list(adapt_delta = 0.9999,
                   stepsize = 0.001,
                   max_treedepth = 20),
    iter = 3000,
    chains = 4
  )

summary(m2)

plot(m2)

pp_check(m2)

plot(pd(m2))

pander(equivalence_test(m2))

# save the model for figures in the paper
save(m2, file = here("data/m2.Rda"))
```

# Colophon
```{r sessioninfo}
sessioninfo::session_info()
```
