---
title: "Initial Analysis"
author: "Adam H Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{initial_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

# Import article evaluations

```{r}
rrpp <- gsheet::gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
)
```

## Unnest the software that were used

```{r}
library(magrittr)
library(tidyr)
rrpp <- 
  rrpp %>%
  unnest(software_used = strsplit(software_used, ", "))
```

# Visualise evaluations

## Article classes

```{r}
library(ggplot2)

ggplot(rrpp, aes(x = art_class)) +
  geom_bar(stat = "count") +
  xlab("Class(es)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Article Classification")
```

## Computational methods available

```{r}
ggplot(rrpp, aes(x = comp_mthds_avail)) +
  geom_bar() +
  ggtitle("Computational Methods Availability") +
  xlab("Score")
```

## Software availability

Was the software used readily available and preferably open-source?

```{r}
ggplot(rrpp, aes(x = software_avail)) +
  geom_bar() +
  ggtitle("Software Methods Availablity") +
  xlab("Score")
```

## Data availability

Was the data made available?

```{r}
ggplot(rrpp, aes(x = data_avail)) +
  geom_bar() +
  ggtitle("Data Availability") +
  xlab("Score")
```

## Software citations

Was the software that was used properly cited?

```{r}
ggplot(rrpp, aes(x = software_cite)) +
  geom_bar() +
  ggtitle("Software Cited") +
  xlab("Score")
```

## Software used (cited)

```{r}

# count and sort top 10 software cited
tab <- table(rrpp$software_used)
tab_s <- sort(tab)
top10 <- tail(names(tab_s), 10)
top_software <- subset(rrpp, software_used %in% top10)
top_software$software_used <- factor(top_software$software_used,
                                     levels = rev(top10))


ggplot(top_software, aes(x = software_used)) +
  geom_bar() +
  ggtitle("Top 10 Software Used") +
  xlab("Software") +
  ylab("Count") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Reproducibility score

What is the combined reproducibility score, a maxiumum of 12 is possible.

```{r}
ggplot(rrpp, aes(x = reproducibility_score)) +
  geom_bar() +
  ggtitle("Combined Reproducibility Score") +
  xlab("Score")
```

## Article class effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = art_class)) +
  geom_boxplot() +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Article Class Effect on Reproducibility") +
  xlab("Class(es)") +
  ylab("Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Journal effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = abbreviation)) +
  geom_boxplot() +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Journal Effect on Reproducibility") +
  xlab("Journal") +
  ylab("Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Evaluator effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = assignee)) +
  geom_boxplot() +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Evaluator Effect on Reproducibility Score") +
  xlab("Evaluator") +
  ylab("Score")
```

## Five year impact factor effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(round(IF_5year, 2)))) +
  geom_boxplot() +
  ggtitle("Five Year IF Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score")
```

## Journal open access effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = open)) +
  geom_boxplot() +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Open Access Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score")
```

## Journal reproducibility instructions effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(repro_inst))) +
  geom_boxplot() +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Reproducibility Instructions Effect on Reproducibility Score") +
  xlab("Reproducibility Instructions Score") +
  ylab("Score")
```
