---
title: "Initial Analysis"
author: "Adam H Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{initial_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

# Import article evaluations

```{r}
rrpp <- gsheet::gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
)
```

## Calculate reproducibility score

```{r}
library(dplyr)

rrpp <-
  rrpp %>%
  mutate(
    reproducibility_score =
      if_else(
        data_avail > 0,
        na.omit(comp_mthds_avail) +
          na.omit(software_avail) +
          na.omit(software_cite) +
          data_avail,
        as.integer(data_avail),
        as.integer(0)
      )
  )
```

## Unnest the software that were used

Create a tidy data frame of the data by unnesting software used as in many cases
multiple software packages were used, so will end up with multiple rows for same
article, one for each software.

```{r}
library(magrittr)
library(tidyr)
rrpp <- 
  rrpp %>%
  unnest(software_used = strsplit(software_used, ", "))
```

# Visualise evaluations

## Article classes

```{r}
library(ggplot2)

ggplot(rrpp, aes(x = art_class)) +
  geom_bar(stat = "count") +
  xlab("Class(es)") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Article Classification")
```

## Computational methods available

```{r}
ggplot(rrpp, aes(x = comp_mthds_avail)) +
  geom_bar() +
  ggtitle("Computational Methods Availability") +
  xlab("Score")
```

## Software availability

Was the software used readily available and preferably open-source?

```{r}
ggplot(rrpp, aes(x = software_avail)) +
  geom_bar() +
  ggtitle("Software Availablity") +
  xlab("Score")
```

## Data availability

Was the data made available?

```{r}
ggplot(rrpp, aes(x = data_avail)) +
  geom_bar() +
  ggtitle("Data Availability") +
  xlab("Score")
```

## Software citations

Was the software that was used properly cited?

```{r}
ggplot(rrpp, aes(x = software_cite)) +
  geom_bar() +
  ggtitle("Software Cited") +
  xlab("Score")
```

## Software used (cited)

Count and sort top 10 software packages cited. There are likely others that are
used, but they have not been properly identified by the authors.

```{r}
tab <- table(rrpp$software_used)
tab_s <- sort(tab)
top10 <- tail(names(tab_s), 17) # checking the table, there are several ties
top_software <- subset(rrpp, software_used %in% top10)
top_software$software_used <- factor(top_software$software_used,
                                     levels = rev(top10))


ggplot(top_software, aes(x = software_used)) +
  geom_bar() +
  ggtitle("Top 10 Software Used") +
  xlab("Software") +
  ylab("Count") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Reproducibility score

The reproducibility score was calculated as the sum of the scores for computational
method availability, 

```{r}
ggplot(rrpp, aes(x = reproducibility_score)) +
  geom_bar() +
  ggtitle("Combined Reproducibility Score") +
  xlab("Score")
```

## Article class effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = art_class)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Article Class Effect on Reproducibility") +
  xlab("Class(es)") +
  ylab("Score") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Journal effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = abbreviation)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Journal Effect on Reproducibility") +
  xlab("Journal") +
  ylab("Score") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Evaluator effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = assignee)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Evaluator Effect on Reproducibility Score") +
  xlab("Evaluator") +
  ylab("Score")
```

## Five year impact factor effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(round(IF_5year, 1)))) +
  geom_boxplot(outlier.shape = NA) +
  ggtitle("Five Year IF Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score")
```

## Journal open access effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = open)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Open Access Effect on Reproducibility Score") +
  xlab("Impact Factor") +
  ylab("Score")
```

## Journal reproducibility instructions effect on reproducibility score

```{r}
ggplot(rrpp, aes(y = reproducibility_score,
                 x = as.factor(repro_inst))) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.25, alpha = 0.5) +
  ggtitle("Reproducibility Instructions Effect on Reproducibility Score") +
  xlab("Reproducibility Instructions Score") +
  ylab("Score")
```
