---
title: "Initial Analysis"
author: "Adam H Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{initial_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
library(ggplot2)
```

# Import article evaluations

```{r}
rrpp <- gsheet::gsheet2tbl(
  "https://docs.google.com/spreadsheets/d/19gXobV4oPZeWZiQJAPNIrmqpfGQtpapXWcSxaXRw1-M/edit#gid=1699540381"
)
```

# Visualise evaluations

## Article classes

```{r}
ggplot(rrpp, aes(x = art_class)) +
  geom_histogram(stat = "count") +
  xlab("Class(es)") +
  scale_x_discrete(labels = c("Applied","Applied, Fundamental, Molecular","Applied, Fundamental","Applied, Molecular","Fundamental, Molecular", "Fundamental", "Molecular", "NA")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ggtitle("Article Classifications")
```

## Computational methods available

```{r}
ggplot(rrpp, aes(x = comp_mthds_avail)) +
  geom_histogram() +
  ggtitle("Computational Methods Available") +
  xlab("Score")
```

## Software availability

Was the software used readily available and preferably open-source?

```{r}
ggplot(rrpp, aes(x = software_avail)) +
  geom_bar() +
  ggtitle("Computational Methods Available?") +
  xlab("Score")
```

## Data availability

Was the data made available?

```{r}
ggplot(rrpp, aes(x = data_avail)) +
  geom_bar() +
  ggtitle("Data Available?") +
  xlab("Score")
```

## Software citations

Was the software that was used properly cited?

```{r}
ggplot(rrpp, aes(x = software_cite)) +
  geom_bar() +
  ggtitle("Software Citations") +
  xlab("Score")
```

## Reproducibility score

What is the combined reproducibility score, a maxiumum of 12 is possible.

```{r}
ggplot(rrpp, aes(x = reproducibility_score)) +
  geom_bar() +
  ggtitle("Combined Reproducibility Score") +
  xlab("Score")
```
