---
title: "Analysis of Publication Year Effect"
author: "Adam H. Sparks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Analysis of Publication Year Effect}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{brms}
  %\VignetteDepends{bayestestR}
  %\VignetteDepends{bayesplot}
  %\VignetteDepends{ggplot2}
  %\VignetteDepends{here}
  %\VignetteDepends{pander}
  %\VignetteDepends{sessioninfo}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_chunk$set(fig.width = 6.4, fig.height = 6.4)
```

This vignette documents the analysis of the data gathered from surveying 21 journals and 450 articles in the field of plant pathology for their openness and reproducibility and the effect that the publication year had on that score.

# Set-up Workspace

Load libraries used and setting the _ggplot2_ theme for the document.

```{r load-libraries, message=FALSE}
library("brms")
library("bayestestR")
library("bayesplot")
library("ggplot2")
library("here")
library("pander")
library("Reproducibility.in.Plant.Pathology")

options(mc.cores = parallel::detectCores())
theme_set(theme_classic())
```

## Import Data

Data are imported and the base level is set to _Molecular Plant Pathology_, the journal with the highest five-year impact factor that will be used as the intercept in the following models.

```{r import-notes}
rrpp <- import_notes()
```

## Notes

All models are using the same priors.

Because of the amount of zero values in the `reproducibility_score` a `hurdle_gamma()` family is used for all models as well.

### Priors

The priors are fairly flat.

```{r priors}
priors <- prior_string("normal(0, 10)")
```

## Year Effect Model

Test the effect that year of publication had on the reproducibility score.
Here, `year` is a fixed effect, `journal` and `assignee` are assigned as random effects.

```{r year}
m6 <-
  brm(
    formula = reproducibility_score ~  year + (1 | journal) + (1 | assignee),
    data = rrpp,
    seed = 25,
    prior = priors,
    family = "hurdle_gamma",
    control = list(adapt_delta = 0.9999),
    iter = 3000,
    chains = 4
  )

summary(m6)

plot(m6)

pp_check(m6)

plot(pd(m6))

pander(equivalence_test(m6))

# save the model for figures in the paper
save(m6, file = here("inst/extdata/m6.Rda"))
```

# Colophon
```{r sessioninfo}
sessioninfo::session_info()
```
