---
title: "Criteria for Evaluating Reproducibility"
author: "Adam H Sparks and Emerson M Del Ponte and Zachary S L Foster and Niklaus J. Grünwald"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Criteria for Evaluating Reproducibility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Key for data collection

## Reproducibility score

#### "year"

Year the article was published.
Entered as a 4-digit number.

#### "vol"

journal volume.

#### "issue"

journal issue.

#### "start_page" 

The page the article started on. 
Entered as a number without commas.
If the journal does not have page numbers, enter `NA`.

#### "last_page" 

The page the article ends on. 
Entered as a number without commas.
If the journal does not have page numbers, enter `NA`.

#### "assignee"

The person evaluating the paper. 
One of:

* `Adam`
* `Emerson`
* `Zach`
* `Nik`

#### "doi"

The doi for the article.
If the article does not have a doi, enter `NA`.

#### "if"

The 5-year impact factor of the journal. 
Entered as a number. Nik entered all values.

#### "page_charges"

How much it costs to publish in the journal?
Entered as a number in dollars without dollar sign?
> This is hard to do. Some journals have choice of open access APC or page charges
> Agree, not sure that it adds much to our work.

#### "country"

The country of the publisher.
Entered as a 3 letter ISO code (e.g. Netherlands = `NLD`)?
> Would this make more sense as the country the correspondiong author works in?
> That makes sense, we could do that -AS

#### "open"

Whether the journal is open-access or not. 
Entered as `TRUE`/`FALSE`/`BOTH`. 

#### "repro_inst"

Does the journal have guidelines for reproducibility? 
Entered as `TRUE`/`FALSE`. 

#### "iss_per_year"

The number of articles per year the journal publishes.
Entered as a number without commas.

#### "art_class"

What kind of research the article describes. 
One or more of the following:

* `Fundamental`
* `Applied`
* `Molecular`

Entered as a comma-separated list with no spaces.

For example: `Applied,Molecular`

#### "supl_mats"

Does the article supply supplemental materials??
I am not sure what this column is for..
> Are supplmental materials avaiable for the article? -AS

#### "anlysis_auto"

Analysis automation score.
Entered as a number between `0` and `4`.

0. All steps were performed manually with no cohesive document describing exactly what was done
1. Steps were performed manually, but with a detailed record (e.g. pasted commands in a text file)
2. A set of runnable scripts were used, but have to be executed individually or the outputs require manual modifications
3. A makefile or master script was provided that runs the entire analysis from raw data to published results


#### "data_avail"

Raw data availability score.
Entered as a number between `0` and `4`.

0. Not available or not mentioned in the publication

1. Available upon request to author

2. Online, but inconvenient/non-permanent (e.g. login needed, pay wall, FTP server, personal lab website)

3. Freely available online to anonymous users for foreseeable future


#### "data_annot"

Raw data annotation score.
Entered as a number between `0` and `4`.

0. No annotation
1. The structure/content of the data is clear, but the relevance to the study is not
2. Fully understandable in the context of the paper
3. Fully understandable without reading the paper

#### "data_tidy"

Raw data tidiness score.
Entered as a number between `0` and `4`.

0. Not easily parsed with code or loaded by standard office software (e.g. unstructured raw text or binary equipment outputs or no raw data)
1. Difficult, but possible, to parse with code or manipulate with standard office software (i.e. you technically could, but would not want to)
2. Able to parse using code with minimal clean-up (e.g. you might need a few extra lines of code for clean up or do a few extra steps to work with your operating system. An example would be a text file with multiple tables)
3. Tidy data in a standardized format (e.g. tsv) that is loaded correctly without clean-up or using uncommon parsing tools.


#### "comp_meth_avail"

Computational methods availability score.
Entered as a number between `0` and `4`.

0. Not available or not mentioned in the publication
1. Available upon request to author
2. Online, but inconvenient/non-permanent (e.g. login needed, pay wall, FTP server, personal/lab website)
3. Freely available online to anonymous users for foreseeable future

#### "software_avail"

Availability of software used score.
Entered as a number between `0` and `4`.

0. Not available or not mentioned in the publication
1. Uses expensive proprietary software that only institutions would typically purchase (i.e. ArcGIS standard is $7000)
2. Uses proprietary software that most individuals can afford (e.g. Excel, Matlab? ($500))
3. Uses entirely open source and free software (e.g. R).

#### "software_citation"

Citation of software used score.
Entered as a number between `0` and `4`.

0. Not available or not mentioned in the publication
1. Software mentioned by name only
2. Attempts at citing
3. Properly cited


## Final reproducibility score

Each article will be scored on a set of defined reproducibility criteria.
The reproducibility score will be the sum of the scores for each criteria.
Thus a perfect score would be 30, scoring three in all ten categories.

## Example of reproducibility `tibble`

Using the scoring system and journal classification, the final `tibble` will look something like this example:

```{r}
reproducibility <- tibble::tibble(
  Article = "The Area Under the Disease Progress Stairs: Calculation, Advantage, and Application",
  DOI = "PHYTO-07-11-0216",
  Journal = "Phytopathology",
  Authors =  "Ivan Simko and Hans-Peter Piepho",
  Year = 2012,
  Vol = 102,
  Iss = 4,
  pp = "381-389",
  IF = 3.011,
  Page_charges = 130,
  Country =  "USA",
  Open_or_Restricted = "Optional",
  Reproducibility_instructions = FALSE,
  Iss_per_Year = 12,
  Article_class = "Fundamental",
  Supl_mats = TRUE,
  Comp_methods_availability = 2,
  Software_availability = 1,
  Software_citation = 3,
  Analysis_automation = 0,
  Data_availability = 0,
  Data_annotation = 0,
  Data_tidiness = 0
)

reproducibility <- dplyr::mutate(reproducibility,
                                 Reproducibility_score = sum(Comp_methods_availability,
                                                             Software_availability,
                                                             Software_citation,
                                                             Analysis_automation,
                                                             Data_availability,
                                                             Data_annotation,
                                                             Data_tidiness))

reproducibility

reproducibility$Reproducibility_score
```
