---
title: "Journal Article Sampling Methodology"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Creating a sample of articles

The top 20 journals in the discipline of plant pathology were selected according to Google Scholar's ranking by h-index, (https://scholar.google.com.au/citations?view_op=top_venues&hl=en&vq=bio_plantpathology).

100 articles are chosen at random with the assumption that journals publish an average 10 articles per issue, and using a confidence level of 95% and confidence interval of 10% we only need 88 samples, so to round it up and make it even, we'll select 100 articles over the last five years from a population that should be ~1000.

## R setup
Set up the R environment

```{r library, message=FALSE}
library(dplyr)

set.seed(27)
```
## Import data
The list of the top 20 plant pathology journals was retrieved from Google Scholar on December 5, 2016 and saved as a CSV file for reproducibility.

```{r journal_list}
journal_list <- read.csv("../data/Google Scholar Top 20 Plant Pathology Journals 05-12-2016.csv")

journal_list[1:20, -4] # drop h-index median value just to tidy things up.

journal_list[1:10, ] # select the top ten journals in plant pathology only
```

## Create random lists
Create a randomised list of the journals

```{r journal_sample_order}
journals <- as.data.frame(sample(1:10, 100, replace = TRUE))
names(journals) <- "Rank"
# reorder joural list
journals <- left_join(journals, journal_list, "Rank")[, -c(3:4)]
```

## Randomly select articles
Generate a random list of years between 2012 and 2016 and a random list of start pages between 1 and 150 since some journals start numbering at 1 with every issue. Then bind the columns of the randomised list of journals with the randomised years and page start numbers. This then assumes that there is no temporal effect, i.e., the time of year an article is published does not affect whether or not it is reproducible.

*How to handle reviews or letters?*

```{r years_and_articles}

year <- sample(2012:2016, 100, replace = TRUE)

start_page <- sample.int(150, 100)

journals <- cbind(journals, year, start_page)

journals[1:100, -1]
```


(Morphological and biochemical responses of five tobacco cultivars to simultaneous infection with Pythium aphanidermatum and Meloidogyne incognita
Mujeebur Rahman KHAN, Ziaul HAQUE)[http://www.fupress.net/index.php/pm/article/view/11386]
(The Periplasmic PDZ Domain–Containing Protein Prc Modulates Full Virulence, Envelops Stress Responses, and Directly Interacts with Dipeptidyl Peptidase of Xanthomonas oryzae pv. oryzae)[http://apsjournals.apsnet.org/doi/abs/10.1094/MPMI-08-13-0234-R]
